%-------------------------
% Resume in Latex
% Author : Aleksei Lapin
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage[russian,english]{babel}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{outlines}
\usepackage{ifthen}
\usepackage{xltabular}
\usepackage{graphicx}
\usepackage{fontawesome5} % icons
\input{glyphtounicode}
\usepackage[export]{adjustbox}
\usepackage{geometry}
\geometry{
  a4paper,
  top=20mm, 
  right=20mm, 
  bottom=15mm, 
  left=20mm
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBold}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheadingItem}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} | {#2} & \textit{\small #3} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\clink[1]{{\usefont{T1}{lmtt}{m}{n} #1 }}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabularx}{\linewidth}{@{}m{0.8\textwidth} m{0.2\textwidth}@{}}
  {
      \huge{\textbf{Aleksei Lapin}} \newline
      \small{
          \clink{
              \href{mailto:a.lapin03@gmail.com}{\faEnvelope~\underline{a.lapin03@gmail.com}} \textbf{ | }
              {\fontdimen2\font=0.75ex \href{tel:+79217770608}{\faPhone~\underline{+7 (921) 777-06-08}}}\textbf{ | }
              \href{https://github.com/AaLexUser}{\faGithub~\underline{github.com/AaLexUser}}
          } 
          \newline
          Saint-Petersburg, Russia
      }
  } & 
  {
      \hfill
      \hfill
  }
\end{tabularx}
\vspace{-15pt}
\section{ }
I am a 3rd year student at ITMO University, studying for a bachelor's degree in System and Applied Software. I am passionate about low-level programming, operating systems as well as web development and machine learning.


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://en.itmo.ru/}{ITMO University}}{Saint-Petersburg, Russia}
      {\href{https://abit.itmo.ru/en/program/bachelor/system_software}{Bachelor of System and Applied Software}}{Sep 2021 -- July 2025}
      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading{
    \href{https://github.com/AaLexUser/ITMO-2-course/tree/main/Computational-mathematics/compl-math-lab-4}
    {Function approximation program}}{\textit{Apr -- May 2023}}{ะก++, SFML}{ }
    \resumeItemListStart
      \resumeItemNoBold{The program finds a function that is the best approximation of a given tabular function using the least squares method.}
      \resumeItemNoBold{Achieved interactive graph interaction (moving, zooming, adding graphs per window) by writing an \textbf{SFML-based} library.}
    \resumeItemListEnd

    \resumeSubheading{
    \href{https://github.com/AaLexUser/ITMO-2-course/tree/main/Programming-languages/assignment-5-sepia-filter}
    {Sepia filter in C and Assembler}}{\textit{January 2023}}{C, x86\_64asm} { }
    \resumeItemListStart
      \resumeItemNoBold{Achieved 10 times faster assembly language program execution than C Implementation by using \textbf{SSE processor vector instructions}.}
      \resumeItemNoBold{Implemented library for working with \textbf{BMP} files of pictures.}
    \resumeItemListEnd

    \resumeSubheading{
    \href{https://github.com/AaLexUser/ITMO-2-course/tree/main/Web-programming/web-4}
    {Point Application}}{\textit{Dec -- Feb 2023}}{Java, TypeScript, React, Redux, Spring Boot, Oracle}{ }
    \resumeItemListStart
      \resumeItemNoBold{Web application designed to create and manage points on the chart, as well as view points of other users of the site.}
      \resumeItemNoBold{Developed a \textbf{RESTful API}, using \textbf{Spring Boot} architecture to handle requests and responses.}
      \resumeItemNoBold{Implemented \textbf{JWT token-based} authentication using \textbf{Spring Security}.}
      \resumeItemNoBold{Used \textbf{Spring Data} to interact with \textbf{Oracle DBMS} by mapping Java objects to tables.}
    \resumeItemListEnd

\resumeSubheading{
    \href{https://github.com/AaLexUser/Route-manager-application}
    {Route Manager}}{\textit{Feb -- Oct 2022}}{Java Core, Stream API, Reflection API, PostgreSQL, SLF4J}{ }
    \resumeItemListStart
      \resumeItemNoBold{Client-server application designed to store user routes.}
      \resumeItemNoBold{Realized data exchange between client and server via \textbf{TCP} protocol.}
      \resumeItemNoBold{Implemented \textbf{multithreading} reading requests, processing and sending responses on the server.}
      \resumeItemNoBold{Developed my own library for automatic dependency injection using \textbf{DI (Dependency injection)} using \textbf{Java Reflection API}.}
      \resumeItemNoBold{Used \textbf{PostgreSQL database} to store data.}
      \resumeItemNoBold{Implemented event logging using the \textbf{slf4j} library.}
      \resumeItemNoBold{Realized password hashing with the \textbf{SHA-256} algorithm.}
      \resumeItemNoBold{Used \textbf{Java Collections} for efficient data storage.}
      \resumeItemNoBold{Used \textbf{Java's Stream API} and lambda expressions to process data efficiently.}


    \resumeItemListEnd

\resumeSubHeadingListEnd 

\section{Awards}
\resumeSubHeadingListStart
  \resumeSubheading{
    \href{https://ftc-events.firstinspires.org/2019/team/12529\#awards}
    {First Russia Robotics Championship}}{Krasnoyarsk, Russia}
    {Think Award Winner as part of the KTM team.}{February 2020}
    
\resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Programming Languages}{C, C++, x86\_64asm, Java, Python, SQL (PostgreSQL), JavaScript, HTML/CSS}
   \resumeSubItem{Frameworks}{Spring Boot, Spring, Spring Data, Spring Security}
   \resumeSubItem{Libraries}{React, Pandas, NumPy, Matplotlib, SFML}
   \resumeSubItem{Developer Tools}{Git, GitHub Actions, Gradle, Maven, CLion, PyCharm, IntelliJ, Webstorm, Jupyter Notebook, GoogleCollab}
   \resumeSubItem{Operating Systems}{Linux, UNIX, Windows}
 \resumeSubHeadingListEnd
 \section{Additional Information}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}{English -- B1}
 \resumeSubHeadingListEnd
\end{document}
